---
title: "Homework1_24206239"
author: "Jing Sun"
format: pdf
execute:
  echo: false
  warning: false
  message: false
---

# Second change to update
# **1. Introduction**

I'm using the *Iris* dataset for this homework1. It's a famous dataset which is built-in dataset in R with **150 observations** of flowers from three species: *setosa*, *versicolor*, and *virginica*. Each flower is described by **four features**: sepal length, sepal width, petal length, and petal width (in cm).

In the rest of this report, I look at the relationship between **petal length** and **petal width**, which helps to show how the species differ.

# **2. Method**

I first explored the data briefly using `head()`, `summary()`, and `table()` to check the structure and basic statistics before making the plot:

## **Exploring the Data**

```{r}
head(iris)
summary(iris[, 3:4])
table(iris$Species)
```

From the output above, we can obtain these information:

-   The dataset has **150 rows** and **5 columns**.
-   Each species appears exactly **50 times**.
-   The average petal length is around **3.76 cm** and average petal width is about **1.20 cm**.
-   *Setosa* tends to have much smaller petals than *virginica*, as seen clearly in the summary and scatter plot.

# **3. Scatter Plot: Petal Length vs Petal Width**

I drew this scatter plot to show how petal length and width vary across species, since that’s the main focus of this report:

```{r}
library(ggplot2)

ggplot(iris, aes(x = Petal.Length, y = Petal.Width, color = Species)) +
  geom_point(size = 3, alpha = 0.8) +
  labs(
    title = "Petal Length vs Petal Width by Species",
    x = "Petal Length (cm)",
    y = "Petal Width (cm)"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14, hjust = 0.5),
    axis.title = element_text(size = 12),
    legend.title = element_text(face = "bold")
  )
```

## **Plot Description**

The scatter plot shows a clear separation between the three iris species:

-   *Setosa* flowers have short and narrow petals.
-   *Versicolor* falls in the mid-range.
-   *Virginica* flowers have the longest and widest petals.

This suggests that petal size is a strong indicator for classifying iris species.
